---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.align = "center",
    fig.path = "README-"
)
```

# `JDCruncheR`

[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/JDCruncheR)](https://cran.r-project.org/package=JDCruncheR)
[![Linting code](https://github.com/InseeFr/JDCruncheR/actions/workflows/lint.yaml/badge.svg)](https://github.com/InseeFr/JDCruncheR/actions/workflows/lint.yaml)

## Français 🇫🇷

### Présentation

Le but premier du package `JDCruncheR` est de fournir un accès rapide et facile au cruncher (`JWSACruncher`) depuis R. Le cruncher est un outil de mise à jour des workspaces de JDemetra+ sans avoir à ouvrir la GUI (Graphical User Interface). La dernière version peut être téléchargée ici : https://github.com/jdemetra/jwsacruncher/releases. Pour plus d'information, vous pouvez visiter la page [wiki](https://github.com/jdemetra/jwsacruncher/wiki).

Avec `JDCruncheR`, vous pouvez aussi générer des *bilans qualité* utilisant l'output du cruncher. Ce bilan est un résumé des diagnostiques de la désaisonnalisation. Il peut être utilisé pour repérer les séries les plus problématiques qui nécessitent une analyse plus fine. Cela est très utile lorsqu'on a beaucoup de séries à désaisonnaliser.

### Installation

Pour obtenir la version en cours de développement depuis GitHub :

```{r fr-gh-devel-installation, eval = FALSE}
# Si le package remotes n'est pas installé
# install.packages("remotes")

# Installer la version en cours de développement depuis GitHub
remotes::install_github("InseeFr/JDCruncheR")
```

Pour obtenir la dernière release stable du package, il y a 2 méthodes d'installation du package `JDCruncheR` :
    
- directement depuis GitHub :

```{r fr-gh-stable-installation, eval = FALSE}
# Si le package remotes n'est pas installé
# install.packages("remotes")

# Installer la dernière version stable disponible sur GitHub
remotes::install_github("InseeFr/JDCruncheR@*release")

# Sur les ordinateurs Insee
install.packages("JDCruncheR", repos = "https://nexus.insee.fr/repository/r-public/")
```

- depuis le dossier compressé **.zip** ou **.tar.gz**, qui peuvent être trouvés ici : https://github.com/InseeFr/JDCruncheR/releases. Pour plus d'informations sur l'installation et la configuration du package `JDCruncheR`, vous pouvez visiter la page [wiki](https://github.com/jdemetra/jwsacruncher/wiki)

Pour une description plus complète des packages R pour JDemetra+ voir le document de travail Insee [Les packages R pour JDemetra+ : une aide à la désaisonnalisation](https://www.insee.fr/fr/statistiques/5019786)


## English 🇬🇧

### Overview

The primary objective of the `JDCruncheR` package is to provide a quick and easy access to the JDemetra+ cruncher (`JWSACruncher`) from R. The cruncher is a tool for updating JDemetra+ workspaces, without having to open the graphical user interface. The latest version can be downloaded here: <https://github.com/jdemetra/jwsacruncher/releases>. For more information, please refer to the [wiki page](https://github.com/jdemetra/jwsacruncher/wiki).

With `JDCruncheR`, you can also generate a *quality report* based on the cruncher's output. This report is a formatted summary of the seasonal adjustment process main diagnostics and parameters. It can be used to spot the most problematic series which will require a finer analysis. This is most useful when dealing with a large number of series.

### Installation

To get the current development version from GitHub:

```{r en-gh-devel-installation, eval = FALSE}
# If remotes packages is not installed
# install.packages("remotes")

# Install development version from GitHub
remotes::install_github("InseeFr/JDCruncheR")
```

To get the current stable version (from the latest release), there are two ways to install the `JDCruncheR` package:
    
- directly from GitHub :

```{r en-gh-stable-installation, eval = FALSE}
# If remotes packages is not installed
# install.packages("remotes")

# Install the last stable release from GitHub
remotes::install_github("InseeFr/JDCruncheR@*release")

# on Insee computer
install.packages("JDCruncheR", repos = "https://nexus.insee.fr/repository/r-public/")
```

- from the **.zip** or **.tar.gz** compressed folder, that can both be found here: : https://github.com/InseeFr/JDCruncheR/releases. For more informations on installing and configuring the `JDCruncheR` package, you can visit the [wiki](https://github.com/jdemetra/jwsacruncher/wiki) page.

For a more comprehensive description of the R packages for JDemetra+ check the Insee working paper [R Tools for JDemetra+: Seasonal adjustment made easier](https://www.insee.fr/en/statistiques/5019812)
