---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  fig.align="center"
)
```

# JDCruncheR

The primary objective of the JDCruncheR package is to provide a quick and easy access to the JDemetra+ cruncher (JWSACruncher) from R. The cruncher is a tool to update a JDemetra+ workspace, without having to open the software itself. 
The latest version can be downloaded here: <https://github.com/jdemetra/jwsacruncher/releases>. Fore more information, please refer to the wiki page: <https://github.com/jdemetra/jwsacruncher/wiki>.

With JDCruncheR, you can also generate a *quality report* based on the cruncher output. This report is a summary of the seasonal adjustment diagnostics. It can be used to spot the most problematic series which will require a finer analysis. This is most useful when dealing with a great number of series, which renders impossible the examination of every diagnostic for every series in a reasonable time. 

There are two ways to install the JDCruncheR package: 

- using the devtools package: 
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("InseeFr/JDCruncheR", build_vignettes = TRUE)
```
- from the **.zip** or **.tar.gz** file, that can both be found here: <https://github.com/InseeFr/JDCruncheR/releases>. For more info on the package installation and the cruncher configuration, please refer to the [wiki](https://github.com/InseeFr/JDCruncheR/wiki).


